Hybrid platforms and bargaining power

### 2023-12-06 src/paper/application.tex
Make figures nicer

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \begin{tikzpicture}[scale=0.8]
            \centering
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                    xtick={0, 1}, ytick=\empty, xlabel={$s$}]
                \addplot[name path=f, blue,ultra thick] {x^2};
                \node[anchor= east] at (axis cs: .9, .9^2) {$N_C f(N_P, sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);

@@

                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Fringe firms are complements}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick=\empty, xlabel={$s$}]
                \addplot[name path=f, blue,ultra thick] {x^0.5};
                \node[anchor=north west] at (axis cs: .6, .6^0.5) {$N_C \tilde{f}(N_P, sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);

@@

        \draw[name path=piF,domain=0.01:5.5,variable=\x,blue,ultra thick] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
        \draw[name path=IF,domain=0.01:5.5,variable=\x,red,ultra thick] plot ({\x},{(\x)/3});
        \node[anchor=north east] at (5,1) {$\pi_F(N_P, n_F)$};
        \node[anchor=south east] at (5,5/3) {$I_F n_F$};

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
                \addplot[name path=f, blue,ultra thick] {ln(1+x)};
                \addplot[name path=tildef, dashed, black] {x};
                \node[anchor=north west] at (axis cs: .5, .4) {$N_C f(N_P, sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \draw[name path=top] (axis cs:0,0.693) -- (axis cs:1,0.693);
                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,0.693);

@@

                \node[anchor=north west] at (axis cs: .05, .65) {Fringe ($F$)};
                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Profit shares with $N_P$}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
                \addplot[name path=f, dashed, black] {ln(1+x)};
                \addplot[name path=tildef, blue,ultra thick] {x};
                \node[anchor=south east] at (axis cs: 0.6, 0.6) {$N_C f(N_P', sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.225, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
                \addplot[name path=f, blue,ultra thick] {sqrt(x)};
                \addplot[name path=tildef, dashed, black] {sqrt(0.5+x)};
                \node[anchor=north west] at (axis cs: .6, 0.77) {$f(0, sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);

@@

                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Profit shares with $N_P = 0$}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.225, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
                \addplot[name path=f, dashed, black] {sqrt(x)};
                \addplot[name path=tildef, blue,ultra thick] {sqrt(0.5+x)};
                \node[anchor=north west] at (axis cs: 0, 0.7) {$f(0.5, sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \draw[name path=top] (axis cs:0,1.225) -- (axis cs:1,1.225);
                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1.225);

@@

        \draw[name path=piF,domain=0.01:5.5,variable=\x,blue,ultra thick] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
        \draw[name path=piF2,domain=0.01:5.5,variable=\x,blue,ultra thick] plot ({\x},{6*((\x)/(0.3+\x))-6*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
        \draw[name path=IF,domain=0.01:5.5,variable=\x,red,ultra thick] plot ({\x},{(\x)/3});

@@

Owing to the additive nature of the total profit function, an even stronger result can be established.
Notice that $f$ has the functional form required for proposition \ref{prop:aggregate_size_additive} with $g(x) = \frac{x}{1+x}, \alpha = V_P, \beta = V_F$.
Therefore, the same proposition implies that
\begin{align*}
    \frac{\partial N_F^*}{\partial N_P} < -\frac{V_P}{V_F},
\end{align*}
that is, an increase in the platform's products leads to a more than proportional reduction in the number of fringe products (\cref{fig:fringe_entry_eq}).\footnote{
    The intuition behind this is demonstrated in \cref{fig:F_F_eq}.
    As the platform's product variety grows, its bargaining power also increases.
    This can be thought of as an increase in (implied) entry fees, which in turn discourages fringe entry.
}
Conversely, equilibrium total aggregate is also decreasing in $N_P$.\footnote{
    The same result also holds true for an increase in $V_P$.
}
As, in this model, consumer welfare is monotone in the total aggregate, this implies that consumer welfare is decreasing in the number of the platform's products (\cref{fig:aggregate_eq}).
Therefore, as opposed to the benchmark model, the platform becoming more hybrid leads to a reduction in consumer welfare.\footnote{
    Unless $V_P N_P$ is high enough that the platform would operate in pure retail mode in the benchmark model, too.
}
\begin{figure}
    \centering
    \begin{tikzpicture}
        \begin{axis}[
                xlabel={$N_P$},
                ylabel={$N_F^*$},
                xmin=0, xmax=1.5, % adjust these values as needed
                ymin=0, ymax=1.4, % adjust these values as needed
                width=10cm, % adjust the width of the plot
                height=6cm, % adjust the height of the plot
                axis lines=left,
                xtick=\empty, ytick=\empty
            ]
            \addplot[color=red,mark=none,very thick] table[x=N_P,y=N_F_bench]{\equilibrium};
            \addplot[color=blue,mark=none,very thick] table[x=N_P,y=N_F]{\equilibrium};
            \addplot[color=black,mark=none,thick,dotted] table[x=N_P,y=N_F_cf]{\equilibrium};
            \legend{Benchmark, Bargaining, Fixed aggregate}
        \end{axis}
    \end{tikzpicture}
    \caption{Equilibrium number of fringe firms as a function of the number of platform products.}
    \label{fig:fringe_entry_eq}
\end{figure}

\begin{figure}
    \centering
    \begin{tikzpicture}
        \begin{axis}[
                xlabel={$N_P$},
                ylabel={$A^*$},
                xmin=0, xmax=1.5, % adjust these values as needed
                ymin=0, ymax=3, % adjust these values as needed
                width=10cm, % adjust the width of the plot
                height=6cm, % adjust the height of the plot
                axis lines=left,
                xtick=\empty, ytick=\empty,
                legend pos=south east
            ]
            \addplot[color=blue,mark=none,very thick] table[x=N_P,y=A_bench]{\equilibrium};
            \addplot[color=red,mark=none,very thick] table[x=N_P,y=A]{\equilibrium};
            \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=A_noF]{\equilibrium};
            \legend{Benchmark, Bargaining, Pure retail}
        \end{axis}
    \end{tikzpicture}
    \caption{Equilibrium aggregate as a function of the number of platform products. Note, that consumer surplus is monotone in the aggregate, therefore this figure also shows ordinal changes in the equilibrium consumer surplus.}
    \label{fig:aggregate_eq}
\end{figure}

\begin{figure}
    \centering
    \begin{tikzpicture}
        \begin{axis}[
                xlabel={$N_P$},
                ylabel={$\pi_P^{t*}$},
                xmin=0, xmax=1.5, % adjust these values as needed
                ymin=0, ymax=0.65, % adjust these values as needed
                width=10cm, % adjust the width of the plot
                height=6cm, % adjust the height of the plot
                axis lines=left,
                xtick=\empty, ytick=\empty,
                legend pos=south east
            ]
            \addplot[color=blue,mark=none,very thick] table[x=N_P,y=pi_P_bench]{\equilibrium};
            \addplot[color=red,mark=none,very thick] table[x=N_P,y=pi_P]{\equilibrium};
            \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=pi_P_noF]{\equilibrium};
            \legend{Benchmark, Bargaining, Pure retail}
        \end{axis}
    \end{tikzpicture}
    \caption{Equilibrium platform profit as a function of the number of platform products.}
    \label{fig:pi_P_eq}
\end{figure}

\begin{figure}
    \centering
    \begin{tikzpicture}
        \begin{axis}[
                xlabel={$N_P$},
                ylabel={$F_F$},
                xmin=0, xmax=1.5, % adjust these values as needed
                ymin=0, ymax=0.65, % adjust these values as needed
                width=10cm, % adjust the width of the plot
                height=6cm, % adjust the height of the plot
                axis lines=left,
                xtick=\empty, ytick=\empty,
                legend pos=north east
            ]
            \addplot[color=blue,mark=none,very thick] table[x=N_P,y=F_F_opt]{\equilibrium};
            \addplot[color=red,mark=none,very thick] table[x=N_P,y=F_F_implied]{\equilibrium};
            \legend{Benchmark (optimal), Bargaining (implied)}
        \end{axis}
    \end{tikzpicture}
    \caption{Optimal/implied entry fee as a function of the number of platform products.}
    \label{fig:F_F_eq}
\end{figure}

>>>>

\definecolor{myblue}{rgb}{0.3, 0.45, 0.69}
\definecolor{myred}{rgb}{0.87, 0.52, 0.32}

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \begin{tikzpicture}[scale=0.8]
            \centering
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                    xtick={0, 1}, ytick=\empty, xlabel={$s$}]
                \addplot[name path=f, black, thick] {x^2};
                \node[anchor= east] at (axis cs: .9, .9^2) {$N_C f(N_P, sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);

@@

                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Fringe firms are complements}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick=\empty, xlabel={$s$}]
                \addplot[name path=f, black, thick] {x^0.5};
                \node[anchor=north west] at (axis cs: .6, .6^0.5) {$N_C \tilde{f}(N_P, sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);

@@

        \draw[name path=piF,domain=0.01:5.5,variable=\x,black,thick] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
        \draw[name path=IF,domain=0.01:5.5,variable=\x,black,dashed,thick] plot ({\x},{(\x)/3});
        \node[anchor=north east] at (5,1) {$\pi_F(N_P, N_F)$};
        \node[anchor=south east] at (5,5/3) {$I_F N_F$};

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
                \addplot[name path=f, black, thick] {ln(1+x)};
                % \addplot[name path=tildef, dashed, black] {x};
                \node[anchor=north west] at (axis cs: .5, .4) {$N_C f(N_P, sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \draw[name path=top] (axis cs:0,0.693) -- (axis cs:1,0.693);
                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,0.693);

@@

                \node[anchor=north west] at (axis cs: .05, .65) {Fringe ($F$)};
                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Profit shares with $N_P$}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
                \addplot[name path=f, dashed, black] {ln(1+x)};
                \addplot[name path=tildef, black, thick] {x};
                \node[anchor=south east] at (axis cs: 0.6, 0.6) {$N_C f(N_P', sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.225, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
                \addplot[name path=f, black, thick] {sqrt(x)};
                % \addplot[name path=tildef, dashed, black] {sqrt(0.5+x)};
                \node[anchor=north west] at (axis cs: .6, 0.77) {$N_C f(0, sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);

@@

                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Profit shares with $N_P = 0$}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.225, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
                \addplot[name path=f, dashed, black] {sqrt(x)};
                \addplot[name path=tildef, black, thick] {sqrt(0.5+x)};
                \node[anchor=north west] at (axis cs: 0.05, 0.75) {$N_C f(N_P', sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \draw[name path=top] (axis cs:0,1.225) -- (axis cs:1,1.225);
                \draw[name path=top_old, dashed] (axis cs:0,1) -- (axis cs:1,1);
                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1.225);

@@

        \draw[name path=piF,domain=0.01:5.5,variable=\x,black, thick] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
        \draw[name path=piF2,domain=0.01:5.5,variable=\x,black, thick] plot ({\x},{6*((\x)/(0.3+\x))-6*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
        \draw[name path=IF,domain=0.01:5.5,variable=\x,black,dashed,thick] plot ({\x},{(\x)/3});

@@

Owing to the additive nature of the total profit function, an even stronger result can be established.
Notice that $f$ has the functional form required for proposition \ref{prop:aggregate_size_additive} with $g(x) = \frac{x}{1+x}, \alpha = V_P, \beta = V_F$.
Therefore, the same proposition implies that
\begin{align*}
    \frac{\partial N_F^*}{\partial N_P} < -\frac{V_P}{V_F},
\end{align*}
that is, an increase in the platform's products leads to a more than proportional reduction in the number of fringe products (\cref{fig:fringe_entry_eq}).\footnote{
    The intuition behind this is demonstrated in \cref{fig:F_F_eq}.
    As the platform's product variety grows, its bargaining power also increases.
    This can be thought of as an increase in (implied) entry fees, which in turn discourages fringe entry.
}
Conversely, equilibrium total aggregate is also decreasing in $N_P$.\footnote{
    The same result also holds true for an increase in $V_P$.
}
As, in this model, consumer welfare is monotone in the total aggregate, this implies that consumer welfare is decreasing in the number of the platform's products (\cref{fig:aggregate_eq}).
Therefore, as opposed to the benchmark model, the platform becoming more hybrid leads to a reduction in consumer welfare.\footnote{
    Unless $V_P N_P$ is high enough that the platform would operate in pure retail mode in the benchmark model, too.
}
\begin{figure}
    \centering
    \begin{tikzpicture}
        \begin{axis}[
                xlabel={$N_P$},
                ylabel={$N_F^*$},
                xmin=0, xmax=1.5, % adjust these values as needed
                ymin=0, ymax=1.4, % adjust these values as needed
                width=10cm, % adjust the width of the plot
                height=6cm, % adjust the height of the plot
                axis lines=left,
                xtick=\empty, ytick=\empty
            ]
            \addplot[color=myred,mark=none,thick] table[x=N_P,y=N_F_bench]{\equilibrium};
            \addplot[color=myblue,mark=none,thick] table[x=N_P,y=N_F]{\equilibrium};
            \addplot[color=black,mark=none,thick,dotted] table[x=N_P,y=N_F_cf]{\equilibrium};
            \legend{Benchmark, Bargaining, Fixed aggregate}
        \end{axis}
    \end{tikzpicture}
    \caption{Equilibrium number of fringe firms as a function of the number of platform products.}
    \label{fig:fringe_entry_eq}
\end{figure}

\begin{figure}
    \centering
    \begin{tikzpicture}
        \begin{axis}[
                xlabel={$N_P$},
                ylabel={$A^*$},
                xmin=0, xmax=1.5, % adjust these values as needed
                ymin=0, ymax=3, % adjust these values as needed
                width=10cm, % adjust the width of the plot
                height=6cm, % adjust the height of the plot
                axis lines=left,
                xtick=\empty, ytick=\empty,
                legend pos=south east
            ]
            \addplot[color=myblue,mark=none,thick] table[x=N_P,y=A_bench]{\equilibrium};
            \addplot[color=myred,mark=none,thick] table[x=N_P,y=A]{\equilibrium};
            \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=A_noF]{\equilibrium};
            \legend{Benchmark, Bargaining, Pure retail}
        \end{axis}
    \end{tikzpicture}
    \caption{Equilibrium aggregate as a function of the number of platform products. Note, that consumer surplus is monotone in the aggregate, therefore this figure also shows ordinal changes in the equilibrium consumer surplus.}
    \label{fig:aggregate_eq}
\end{figure}

\begin{figure}
    \centering
    \begin{tikzpicture}
        \begin{axis}[
                xlabel={$N_P$},
                ylabel={$\pi_P^{t*}$},
                xmin=0, xmax=1.5, % adjust these values as needed
                ymin=0, ymax=0.65, % adjust these values as needed
                width=10cm, % adjust the width of the plot
                height=6cm, % adjust the height of the plot
                axis lines=left,
                xtick=\empty, ytick=\empty,
                legend pos=south east
            ]
            \addplot[color=myblue,mark=none,thick] table[x=N_P,y=pi_P_bench]{\equilibrium};
            \addplot[color=myred,mark=none,thick] table[x=N_P,y=pi_P]{\equilibrium};
            \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=pi_P_noF]{\equilibrium};
            \legend{Benchmark, Bargaining, Pure retail}
        \end{axis}
    \end{tikzpicture}
    \caption{Equilibrium platform profit as a function of the number of platform products.}
    \label{fig:pi_P_eq}
\end{figure}

\begin{figure}
    \centering
    \begin{tikzpicture}
        \begin{axis}[
                xlabel={$N_P$},
                ylabel={$F_F$},
                xmin=0, xmax=1.5, % adjust these values as needed
                ymin=0, ymax=0.65, % adjust these values as needed
                width=10cm, % adjust the width of the plot
                height=6cm, % adjust the height of the plot
                axis lines=left,
                xtick=\empty, ytick=\empty,
                legend pos=north east
            ]
            \addplot[color=myblue,mark=none,thick] table[x=N_P,y=F_F_opt]{\equilibrium};
            \addplot[color=myred,mark=none,thick] table[x=N_P,y=F_F_implied]{\equilibrium};
            \legend{Benchmark (optimal), Bargaining (implied)}
        \end{axis}
    \end{tikzpicture}
    \caption{Optimal/implied entry fee as a function of the number of platform products.}
    \label{fig:F_F_eq}
\end{figure}
